### 2023-06-22 manuscript.tex
title [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/5d37849fa90947eb93bbfe067f9489cc79aa07dd.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/5d37849fa90947eb93bbfe067f9489cc79aa07dd/checks
https://github.com/stain/2022-fdo-paper/actions/runs/5340432870

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/251c1d7a7c7a10ef9206e0a11ed9bb3d24dcf8b1/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/251c1d7a7c7a10ef9206e0a11ed9bb3d24dcf8b1}{stain/2022-fdo-paper@251c1d7}
on June 22, 2023.

>>>>

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/5d37849fa90947eb93bbfe067f9489cc79aa07dd/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/5d37849fa90947eb93bbfe067f9489cc79aa07dd}{stain/2022-fdo-paper@5d37849}
on June 22, 2023.
